\section{Litteraturliste}
\begingroup
\renewcommand{\section}[2]{}%

\begin{thebibliography}{1}
	\subsection{Artikler}
	\bibitem{DTMF}  Bhavannam: Midasala, "DTMF Tone Generation and Detection Using Goertzel Algorithm with MATLAB", I: Proceedings of International Conference on Innovation in Electronics and Communications Engineering, 2013
	
	\subsection{Bøger}
  
  \bibitem{oosa} Ashrafi: Noushin: Hessam. "{\em Object Orient System Analysis and Design.}" Prentice Hall, 2008, Chapter 13
  
  \bibitem{DSP} Tan, Li: Jiang, Jean, "{\em Digital Signal Processeing.}", 2. edition, Elsvier, 2013
  
  \bibitem{AUaP} Larman, Craig, "{\em Applying UML and Patterns.}", Second edition, Prentice Hall, 2008
    
  \bibitem{DCN} Forouzan, Behrouz A., "{\em Data Communications and Networking.}", Fifth edition, McGraw-Hill, 2013
  
	\subsection{Hjemmesider}
  \bibitem{dllein} Kowalk, W.: "CRC Cyclic Redundancy Check Analysing and Correcting Errors". På http://www.uni-oldenburg.de, {http://einstein.informatik.uni-oldenburg.de/papers/CRC-BitfilterEng.pdf} Publiceret 08/2006. Besøgt 15/12/2015

  \bibitem{ross} Ross, Williams N.: "A Painless Giode To CRC Error Detection Algorithms". På ross.net, {http://www.ross.net/crc/download/crc\_v3.txt}, Publiceret 19/8/1993. Besøgt 9/11/2015.
  
  \bibitem{hack} Koopman, Philip: Chakrabarty, Tridib,: "Cyclic Redundancy Code (CRC) Polynomial Selection For Embedded Networks". På http://repository.cmu.edu/, {http://repository.cmu.edu/cgi/viewcontent.cgi?article=1672\&context=isr}, Publiceret 2004. Besøgt 11/12/2015.
  
  \bibitem{barr} Barr, Michael,: "CRC Series, Part 3: CRC Implementation Code in C/C++" På barrgroup.com {http://www.barrgroup.com/Embedded-Systems/How-To/CRC-Calculation-C-Code} Publiceret 02/12/2007. Besøgt 11/12/2015.
  \end{thebibliography}